---
title: "Lab 01 - Hello R"
author: "Graham Overheu"
date: "Jan 22"
output: 
  html_document: 
    fig_height: 3
    fig_width: 6
    theme: cosmo
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

## Exercises

### Exercise 1

There are three columns and 1,846 rows in the data set.

### Exercise 2


```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) + geom_point()
```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
An r-value of -0.06 indicates a very weak negative linear correlation between x and y.

### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
```


```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficients for the dino and star data sets are practically the same with values of -0.064 and -0.063, respectively. With that said, both exhibit very weak negative linear relationships between x and y.

### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
```

```{r}
circle_data %>%
  summarize(r = cor(x, y))
```
The relationship between the x and y variables is very weak and negative, as shown by an r value of -0.07.

### Exercise 5


```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```
```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```





